Exploring graphs with pebbles

### 2016-05-11 paper/main.tex
shorten shorten shorten

This construction of barriers is iteratively and relies on a result from
\cite{0barrier}.
\begin{thm}
  For any $q$ non-cooperative $s$-state agents without pebbles, there exists
  a 3-regular graph $G$ on $\mathcal{O}(qs)$ vertices with the following
  property: There are two edges $\left\{v_1,v_2\right\}$ and
  $\left\{v_3,v_4\right\}$ in $G$, the first labeled 0, such that any of the
  $q$ agents starting in $v_1$ or $v_2$ does not traverse the edge
  $\left\{v_3,v_4\right\}$.
\end{thm}
From this we obtain a $0$-barrier for an agent $\mathcal{A}$ by applying
above theorem to the set of agents
$\left\{\mathcal{A}_{q}\mid q\in Q_{\mathcal{A}}\right\}$ where
$\mathcal{A}_{q}$ has the same behaviour as $\mathcal{A}$ but starts in
state $q$. More formally,
\begin{lem}
  \label{lem:0bar}
  For every $s$-state agent with $p$ pebbles $\mathcal{A}$ there exists a
  $0$-barrier with $\mathcal{O}(s^{2})$ vertices, which is independent of
  the starting state of $\mathcal{A}$.
\end{lem}

>>>>

This construction of barriers is iteratively and relies on a result from
\cite{0barrier} which is used to obtain an initial $0$-barrier.
\begin{lem}
  \label{lem:0bar}
  For every $s$-state agent with $p$ pebbles $\mathcal{A}$ there exists a
  $0$-barrier with $\mathcal{O}(s^{2})$ vertices, which is independent of
  the starting state of $\mathcal{A}$.
\end{lem}
